A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-10 doc/popl2013/evaluation.tex
small edits to evaluation
Removing the circuit description from evaluation since it now has its own section

\subsection{Expressivity}
\label{subsec:expressivity}
We evaluate Legion on three real-world applications.  To qualitatively gauge the 
expressivity of the Legion type system, we introduce each of these applications
by describing features of the Legion type system used in their implementations.

\subsubsection{Circuit Simulation}
\label{subsec:circuit}
Circuit simulates the wires of a large integrated circuit.
% using an RLC model.  
%The computation consists of three phases for each time step: compute the current in each wire using
%an iterative model, updated the charge in each node, and compute the voltage of each node.
The primary data structure is a large irregular graph, which is
dynamically partitioned into pieces to enable parallel simulation.
Our implementation creates separate regions for the wires and
nodes,  which are recursively partitioned into
subregions for pieces of the graph.  The node region is partitioned an additional way to 
describe the sets of ghost nodes required for each piece.  
The information about each piece of the graph is stored
in a region relationship that remembers the disjointness information of each piece
from other pieces.  The tasks for the three phases of the computation use different combinations of
read, write, and reduce privileges as well as exclusive and simultaneous coherence.

@@

These applications show Legion is capable of 
expressing applications with both regular (Fluid,AMR) and irregular (Circuit) pointer data structures.
Being able to dynamically create and partition regions at runtime is crucial to Legion's
ability to handle applications that make runtime decisions about data organization(AMR).  Legion
is able to capture both allocate-then-partition (Circuit) and partition-then-allocate (Fluid) algorithms. 
Having multiple partitions of regions is necessary for describing the many ways 
that data can be accessed (Circuit,AMR).  All the types of privileges and coherence we have
described are needed in different combinations by the applications.  Region relationships
are used in all applications. %, region relationships convey disjointness information.
% despite
%regions being a first-class feature that cannot be fully tracked statically.

>>>>

\subsection{Expressivity}
\label{subsec:expressivity}
We evaluate Legion on three real-world applications.  To qualitatively gauge the 
expressivity of the Legion type system, we introduce these applications
by describing features of the Legion type system used in their implementations.
The Circuit example was already covered in detail in Section~\ref{sec:example}.

%\subsubsection{Circuit Simulation}
%\label{subsec:circuit}
%Circuit simulates the wires of a large integrated circuit.
% using an RLC model.  
%The computation consists of three phases for each time step: compute the current in each wire using
%an iterative model, updated the charge in each node, and compute the voltage of each node.
%The primary data structure is a large irregular graph, which is
%dynamically partitioned into pieces to enable parallel simulation.
%Our implementation creates separate regions for the wires and
%nodes,  which are recursively partitioned into
%subregions for pieces of the graph.  The node region is partitioned an additional way to 
%describe the sets of ghost nodes required for each piece.  
%The information about each piece of the graph is stored
%in a region relationship that remembers the disjointness information of each piece
%from other pieces.  The tasks for the three phases of the computation use different combinations of
%read, write, and reduce privileges as well as exclusive and simultaneous coherence.

@@

These applications show Legion is capable of 
expressing applications with both regular (Fluid,AMR) and irregular (Circuit) pointer data structures.
Being able to dynamically create and partition regions at runtime is crucial to Legion's
ability to handle applications that make runtime decisions about data organization(AMR).  Legion
is able to capture both allocate-then-partition (Circuit) and partition-then-allocate (Fluid) algorithms. 
Having multiple partitions of regions is necessary for describing the many ways 
that data can be accessed (Circuit,AMR).  All the types of privileges and coherence we have
described are needed in different applications.  Region relationships
are used in all applications. %, region relationships convey disjointness information.
% despite
%regions being a first-class feature that cannot be fully tracked statically.
